Advanced Calc Homework \large 1: 1.1: 1,3,5,7,8,11,17, 1.2: 1,4

### 2017-01-27 311/latex/HW1.tex
Add 311 homework almost done.

\section{Problem 1.1}

@@

\textbf{Base case} The base case S(1) states that for $n\in\mathh{N}$, $n-1\in{mathbb}$. This is true by Problem 1.1.7.\\

@@

\section{Problem 1.1.11a}
\textbf{WTS} If $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $a+b \in \mathb{R}\ \mathbb{Q}$.

\textbf{Proof} In search of a contradiction, assume for $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, that $a+b \in \mathbb{Q}$. Then by the definition of rational numbers there exist $m,n \in \mathbb{Z}$ such that $a+b = \frac{m}{n}$. $a$ can be similarly expanded using $x,y \in \mathbb{Z}: $\frac{x}{y}+b = \frac{m}{n}$. We will perform algebra and show this leads to a contradiction:

@@

Because the product and difference of two integers is also an integer, this means b can be expressed as a fraction of two integers. This is the desired contradiction. Thus, if $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $a+b \in \mathb{R}\ \mathbb{Q}$.

\section{Problem 1.1.11b}
\textbf{WTS} If $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $ab \in \mathb{R}\ \mathbb{Q}$.

\textbf{Proof} In search of a contradiction, assume for $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, that $ab \in \mathbb{Q}$. Then by the definition of rational numbers there exist $m,n \in \mathbb{Z}$ such that $ab = \frac{m}{n}$. $a$ can be similarly expanded using $x,y \in \mathbb{Z}: $\frac{x}{y}b = \frac{m}{n}$. This can be rewritten as $b = \frac{my}{nx}$. Because the product of two integers is itself an integer, we have expressed b as a fraction of two integers. This is the desired contradiction. Thus, if $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $ab \in \mathb{R}\ \mathbb{Q}$.

@@

@@

\end{document}

>>>>

\section{Problem 1.1.1}
\textbf{A} False, since $1$ isn't irrational.
\textbf{B} False, since $\sqrt{2}$ is irrational, and thus $2$ cannot be inductive stepped to from $1$.
\textbf{C} False. Consider $a = \sqrt{2}$ and $b = 2 - \sqrt{2}$. Both are irrational, since the sum of a rational and irrational is irrational, but their sum is a rational.
\textbf{D} False for a similar reason: consider $\pi$ and $\frac{1}{\pi}$. Both irrational since rational and irrational numbers combine via multiplication to be irrational, but have a rational product.
\textbf{E} True. ISOAC, let $n^2$ be odd but $n$ even. Thus $\exists k\in\mathbb{N} st n=2k$, so $n^2 = 4k^2 = 2*2k^2$. This is a contradiction, since $n^2$ was supposed to be odd.\\

@@

\textbf{Base case} The base case S(1) states that for $n\in\mathbb{N}$, $n-1\in{mathbb}$. This is true by Problem 1.1.7.\\

@@

\section{Problem 1.1.11a}
\textbf{WTS} If $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $a+b \in \mathbb{R}\ \mathbb{Q}$.

\textbf{Proof} In search of a contradiction, assume for $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, that $a+b \in \mathbb{Q}$. Then by the definition of rational numbers there exist $m,n \in \mathbb{Z}$ such that $a+b = \frac{m}{n}$. $a$ can be similarly expanded using $x,y \in \mathbb{Z}: \frac{x}{y}+b = \frac{m}{n}$. We will perform algebra and show this leads to a contradiction:

@@

Because the product and difference of two integers is also an integer, this means b can be expressed as a fraction of two integers. This is the desired contradiction. Thus, if $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $a+b \in \mathbb{R}\ \mathbb{Q}$.

\section{Problem 1.1.11b}
\textbf{WTS} If $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $ab \in \mathbb{R}\ \mathbb{Q}$.

\textbf{Proof} In search of a contradiction, assume for $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, that $ab \in \mathbb{Q}$. Then by the definition of rational numbers there exist $m,n \in \mathbb{Z}$ such that $ab = \frac{m}{n}$. $a$ can be similarly expanded using $x,y \in \mathbb{Z}: \frac{x}{y}b = \frac{m}{n}$. This can be rewritten as $b = \frac{my}{nx}$. Because the product of two integers is itself an integer, we have expressed b as a fraction of two integers. This is the desired contradiction. Thus, if $a \in \mathbb{Q}$ and $b \in \mathbb{R}\ \mathbb{Q}$, then $ab \in \mathbb{R}\ \mathbb{Q}$.

@@

Then, by the Completeness Axiom, there must exist some $b \in R$ such that $b = Sub(S)$.\\

@@

\section{Problem 1.2.1}
\textbf{A} False. Consider real numbers $1.6$ and $1.8$. There are no integers between these two, thus the integers are not dense.\\
\textbf{B} False. Consider real numbers $-2.0 and -1.0$. There are no positive reals between these two, and thus the positive reals are not dense.\\
\textbf{C} True. The rational numbers are dense in the reals. For reals a, b, where $a > b$, by the Archimedean principle there exists a number $n \in \mathbb{N}$ such that $\frac{1}{n} \leq a-b$. Then $b + \frac{1}{n}$ is between the two. If it is an integer, then $b + \frac{1}{n^2}$ shouldn't be, and is also between the two.

\section{Problem 1.2.4}
\textbf{A} Set $\{1/n | n \in \mathbb{N}\}$
\textit{Maximum} - 1, all $n > 1$ are smaller.\\
\textit{Minimum} - None. For any $1/n$ in the set, $1/(n+1)$ is smaller.\\
\textit{Supremum} - 1. $1/1$ is the largest value in the set.\\
\textit{Infimum} - 0. Any number $\epsilon > 0$ has a number $1\m$ smaller than it, by the Archimedean Principle, so 0 is the largest lower bound.\\

\textbf{B} Set $\{x | x \in \mathbb{R} \mbox{ and } x^2 < 2\}$
\textit{Maximum} - None. For any number $e < \sqrt{2}$, $e + \frac{\sqrt{2}-e}{2}$ is bigger
\textit{Minimum} - Same argument with $-\sqrt{2}$.\\
\textit{Supremum} - $\sqrt{2}$. Anything smaller is in the set, and it isn't in the set.
\textit{Infimum} - $-\sqrt{2}$ by the same argument.\\
\end{document}
